Modelling the Lymphatic Metastatic Progression Pathways of OPSCC from Multi-Institutional Datasets

### 2023-11-29 src/tex/ms.tex
[showyourwork] overleaf sync

>>>>

\begin{figure}
    \centering
    \includegraphics{figures/ranking.pdf}
    \caption{Visual ranking of the investigated graphs w.r.t. their model evidence, computed via thermodynamic integration. Missing are only the two graphs where the arc from \gls{lnl} III to IV was removed. Their respective model evidence fell below $-1528$ and did thus not fit on this figure. In the bottom left corner, we provide a visual reference in analogy to \cref{table:bayes_factor}: E.g., any difference in the model evidence shorter than the first of the three rulers indicates that the improvement is "barely worth a mention".}
    \label{fig:ranking}
\end{figure}
